---
title: "Presentaci칩n Cartera de Creditos"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    social: menu
    source: embed
  runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(haven)
library(labelled)
library(readxl)
library(lubridate)
library(mice)
library(ExPanDaR)
library(GGally)
library(corrplot)
library(ggplot2)
library(explor)
library(cluster) # medoides
library(Kmedians) # medianas
library(factoextra) # visual
library(flexclust)
library(dygraphs)
library(shiny)
library(plotly)
library(ggplot2)
library(kableExtra)

load("BDO_MUESTRA_10.RData")
BD <- BDO_MUESTRA_10 %>% select_if(is.numeric)

```

### An치lisis Descriptivo

```{r}

fig <- plot_ly(BD, y= ~VALOR_ASEGURADO, type = "box", name = "Valor Asegurado") %>%
       add_trace(y = ~MONTO_DESEMBOLSADO, name = "Monto Desembolsado") 

fig
```

***
  
  https://rstudio.github.io/leaflet/
  
  - Interactive panning/zooming

- Compose maps using arbitrary combinations of map tiles, markers, polygons, lines, popups, and GeoJSON.

- Create maps right from the R console or RStudio

- Embed maps in knitr/R Markdown documents and Shiny apps

- Easily render Spatial objects from the sp package, or data frames with latitude/longitude columns

- Use map bounds and mouse events to drive Shiny logic

### MetricsGraphics enables easy creation of D3 scatterplots, line charts, and histograms.

```{r}
mcor <- BDO_MUESTRA_10 %>% select(where(is.numeric)) %>% cor()
corrplot(mcor)

# Calcular los eigenvalores y eigen vectores
m1<-eigen(mcor)
a1<-m1$vectors %*% diag(m1$values) %*% t(m1$vectors)

m<-4
a2<-m1$vectors[,1:m] %*% diag(m1$values)[1:m,1:m] %*% t(m1$vectors[,1:m])
plot(1:length(m1$values),m1$values, type = "b")
pesoL<-(m1$values/sum(m1$values))*100

```

***

Correlaciones

```{r}
kable(round(a2-mcor,5))
```




### An치lisis de K-medias seleccionando variables



```{r}

palette(c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3",
  "#FF7F00", "#FFFF33", "#A65628", "#F781BF", "#999999"))

# Combine the selected variables into a new data frame
selectedData <- reactive({
  BDO_MUESTRA_10[, c(input$xcol, input$ycol)]
})

clusters <- reactive({
  kmeans(selectedData(), input$clusters)
})

renderPlot({
  par(mar = c(5.1, 4.1, 0, 1))
  plot(selectedData(),
       col = clusters()$cluster,
       pch = 20, cex = 3)
  points(clusters()$centers, pch = 4, cex = 4, lwd = 4)
})

```

***

Selecci칩n de variables.

```{r}
selectInput('xcol', 'X Variable', names(BD))

selectInput('ycol', 'Y Variable', names(BD),
                selected=names(BD)[[2]])
    
numericInput('clusters', 'Cluster count', 3,
              min = 1, max = 9)
```

### Analisis k medias con componentes principales

```{r}
BD_num <- BDO_MUESTRA_10%>% select_if(is.numeric)
BDOS<-scale(BD_num)
set.seed(1245)#controlar la aleatoriedad
n2<-kmeans(BDOS,2)# comando de origen
gm <- fviz_cluster(n2, data=BDOS, geom= "point") + theme_minimal() 
gm

```

***

https://plot.ly/ggplot2/

If you use ggplot2, `ggplotly()` converts your plots to an interactive, web-based version! It also provides sensible tooltips, which assists decoding of values encoded as visual properties in the plot.

plotly supports some chart types that ggplot2 doesn't (such as 3D surface, point, and line plots). You can create these (or any other plotly) charts using `plot_ly()`.


### Analisis k medias con componentes principales

```{r}
m5<-princomp(BDO_MUESTRA_10 %>% select_if(is.numeric), cor = T)
BDO_c<-BDO_MUESTRA_10 %>% bind_cols(data.frame(m5$scores))

ggplot(BDO_c, aes(Comp.1,Comp.2, col=DESC_SUCURSAL)) + geom_point(alpha=0.5) + geom_vline(xintercept =  0,linetype="dotted") +
  geom_hline(yintercept = 0,linetype="dotted")
```

***
```{r}

corrplot(
  cor(BDO_c %>% select_if(is.numeric))
)
```

